Open archaeology, open source?

### 2024-02-02 analysis/_05-collaboration.qmd
Clarify fig-collab-features caption

```{r fig-collab-features}
#| fig-cap: Use of GitHub collaboration features in open archaeology repositories
oarch_gh |>
  pivot_longer(c(forks, issues, comments, stars), 
               names_to = "feature", values_to = "n") |>
  mutate(
    feature = factor(feature, c("stars", "comments", "issues", "forks")),
    feature = recode(feature, issues = "Issues and pull requests"),
    feature = fct_relabel(feature, str_to_sentence)
  ) |>
  ggplot(aes(n, feature)) +
  geom_boxplot() +
  scale_x_log10() +
  labs(x = NULL, y = NULL) +
  theme_oarch()
```

>>>>

```{r fig-collab-features}
#| fig-cap: Box plot showing use of GitHub collaboration features in open archaeology repositories
oarch_gh |>
  pivot_longer(c(forks, issues, comments, stars), 
               names_to = "feature", values_to = "n") |>
  mutate(
    feature = factor(feature, c("stars", "comments", "issues", "forks")),
    feature = recode(feature, issues = "Issues and pull requests"),
    feature = fct_relabel(feature, str_to_sentence)
  ) |>
  ggplot(aes(n, feature)) +
  geom_boxplot() +
  scale_x_log10() +
  labs(x = NULL, y = NULL) +
  theme_oarch()
```
